Meta-analysis for the Effect of SSRIs on Anxiety

### 2023-01-23 codebook_dat.Rmd
Analysis. Only necessary changes: different way to read in the reference categories, and excluding four outliers with extreme values for the effect size.

---
title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
output: github_document
---

@@

## Dataset description
The data contains 20 cases and 24 variables.

>>>>

---
title: "Codebook created on 2023-01-23 at 2023-01-23 09:17:39"
output: github_document
---

@@

## Dataset description
The data contains 465 cases and 19 variables.

### 2023-01-23 manuscript/manuscript.Rmd
Analysis. Only necessary changes: different way to read in the reference categories, and excluding four outliers with extreme values for the effect size.

---
title: "Untitled"
output: bookdown::html_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = TRUE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
if(maxz > 3.3) stop("Potential outlier in Y-space")
saveRDS(dat, "dat.RData")
```

@@

```{r, eval = run_everything}
refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

@@

  # Find ref cat
  catvars <- sapply(dfmod, class) == "factor"
  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
  refcat <- data.frame(Variable = names(refcats)[-1],
                       Reference = unlist(refcats[refcats$sample == p, -1]))
  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)

>>>>

---
title: "Meta-analysis for the Effect of SSRIs on Anxiety"
output: bookdown::html_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = FALSE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
if(maxz > 3.3) stop("Potential outlier in Y-space")
dat <- dat[!abs(zscores) > 3.3, ]
saveRDS(dat, "dat.RData")
```

@@

```{r, eval = run_everything}
# refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
# Refcats now provided in different format
refcats <- readxl::read_xlsx("../20230120 SRMA Datasheet Caspar.xlsx", sheet = 2, skip = 1)
refcats <- lapply(samples, function(s){
    refcats[, c(which(names(refcats) == s):(which(names(refcats) == s)+1))]
})
names(refcats) <- samples
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

@@

  # Find ref cat
  # Changed, because reference categories are now provided by researchers
  catvars <- sapply(dfmod, class) == "factor"
  refcat <- as.data.frame(refcats[[p]])
  names(refcat) <- c("Variable", "Reference")
  refcat$Variable <- tolower(refcat$Variable)

  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]

  dfmod[catvars] <- lapply(names(catvars)[catvars], function(c){
    v <- dfmod[[c]]
    relevel(v, ref = refcat$Reference[which(refcat$Variable == c)])
  })
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)
